Toxic Code Snippets on Stack Overflow

### 2018-05-19 cloverflow-tse/cloverflow.tex
Revised until Section 3.4.

Nevertheless, we investigated a crucial parameter setting for clone detection: the minimum clone size threshold.
Choosing a large clone size threshold can reduce the number of false clones reported,
while at the same time creates some false negatives, i.e.~missing some of the true clones.
On the other hand, setting a low threshold results in a larger number of clone
candidate pairs to look at and a higher chance of getting false positives.
It is known that lowering the number of minimum clone lines is harmful to precision.
Moreover, the large number of clone pairs will hinders the full manual
validation of the clones and one needs to rely on sampling of clone pairs.
We started our investigation by using a minimum clone
size of 6 lines, a well-accepted minimum clone size in clone
benchmark~\cite{Bellon2007}. Simian reported 67,172 clone candidate pairs and
SourcererCC reported 7,752 clone candidate pairs. We randomly sampled 382 pairs
from the merged set of 74,148 clone pairs and the first author investigated them. This was
a statistical significant sample with a 95\% confidence level and $\pm 5\%$ confidence interval.
We found 322 trivial clone pairs including \texttt{equals}, \texttt{hashCode}, or getters/setters;
26 non clone pairs, and 34 non-trivial clone pairs.
We then increased the minimum clone size to 10 lines, another well-established 
minimum clone size for large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from Simian and
1,678 clone pairs from SourcererCC. We randomly sampled and manually checked the same amount of 382 pairs
from the merged set of 2,289 clone pairs.
We found 251 trivial clone pairs, 40 non-clone pairs, and 91 non-trivial clone pairs.

The findings from the two samples show that selecting the minimum of 6 lines generated
a large number of clones (74,148 pairs) with more trivial clone pairs, which we were not interesting for this study, 
and fewer non-trivial pairs compared to the minimum of 10 lines.
%To put it another way, lowering the number of clone lines is harmful to precision.
Moreover, the amount of 2,289 clone pairs using minimum of 10 clone lines 
was feasible for manual investigation in the next phase.
Increasing the minimum clone size further will result in a smaller clone subset
but may also remove some of the true clone pairs (generating false negatives).
Thus, we selected the minimum clone size of 10 lines for both Simian and SourcererCC.

%The minimum clone size of 10 lines is
%considered a standard setting for clone detection in large-scale data sets to
%avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or getter and
%setter methods) in the analysis or the manual investigation phase~\cite{Sajnani2016}.  
%We
% performed an analysis to confirm this.
%\begin{figure} 
%	\centering
%	\includegraphics[width=\linewidth]{boxplot_clone_size_combined} 
%	\caption{Size of online code clones.} 
%	\label{fig:boxplotclonesize}
%\end{figure}

%The result is as shown in
%\Cref{fig:boxplotclonesize}. We found that the distribution of the manually
%confirmed true clones 
%mainly cover the size from about 10 to 20 lines. Increasing
%the threshold to be higher than 10 would remove some of the
%true clone pairs.
%
%Regarding decreasing the minimum clone size to be less than 10 lines, we reran
%the two clone detection tools again using a minimum
%clone size of 6 lines, another well-accepted minimum clone size in clone
%benchmark~\cite{Bellon2007}. Simian reported 67,172 clone candidate pairs and
%SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs. 
%With this large amount of clone
%candidate pairs, it is not feasible to manually confirm all of the clones and we
%must rely on sampling. This will result in weaker findings and
%weaker conclusion. Thus, we decide pick the minimum clone size of 10 lines
%to keep the balance between the number of non-trivial clone pairs and the
%feasibility of manual clone investigation.
%We made sure that they 
%detected only non-trivial clones by increasing the minimum clone size to ten
%lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

%We encountered NiCad failures with a few Qualitas projects.~$N_D$
%could not detect clones in \textsf{hibernate} due to clustering
%errors. $N_E$ generated errors during code normalisation for 5
%projects including \textsf{vuze}, \textsf{hibernate},
%\textsf{myfaces}, \textsf{netbeans}, and \textsf{spring}. We have
%contacted the creator of NiCad regarding the issues. They identified
%the issues as problems in the TXL grammar and as problems of long file
%paths, and will be fixed in the next NiCad releases.

The number of online clone pairs reported % by running Simian and NiCad
are presented in \Cref{tab:orig_stats}. Simian reports 721 clone
pairs while SourcererCC reports 1,678 clone pairs. 
SourcererCC reports more clones due to its capability of detecting
clones of type-1 to type-3 while Simian only detects type-1 clones.
The average clone size reported by Simian is
16.61 lines which is slightly smaller than SourcererCC (17.86 lines).

@@

The threshold \textit{t} is crucial for the ok-match because it affects the number
of merged clone pairs. Setting a high \textit{t} value will result in a few ok-match clone pairs
and duplicates of the same clone pairs (which are supposed to be merged) may appear in the merged
clone set. On the other hand, setting a low \textit{t} value will result in many ok-match clone
pairs and some non-duplicate clone pairs may be accidentally merged by only
a few matching lines.
In order to get an optimal $t$ value, we did an analysis by choosing
five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
By setting $t=0.7$ according to Bellon's study, we
found 97 ok-match pairs reported. On the other hand, setting $t$ to 0.1, 0.3,
0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually
checked all the 111 reported pairs. We found one false positive pair and 110
true positive pairs. By raising the $t$ to 0.3 and 0.5, we got rid of the false
positive pair and still retained all the 110 true positive pairs. All the clone
pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a
subset of $t=0.5$. However, since there is a fewer true positive pairs reported
(i.e.~generating false negatives), we ended up leaving some duplicates of the 
same clones in the final merged clone set.
With this analysis, we can see that setting the threshold $t$ to 0.1 is too
relaxed and results in having false positive ok-match pairs, while setting the
$t$ to 0.7 or 0.9 is too strict and generates some false negative pairs. Thus,
we decided to select the $t$ value at 0.5.

Using the ok-match criterion with the threshold \textit{t} of 0.5
similar to Bellon's study~\cite{Bellon2007}, we merge 721 clone pairs from
Simian and 1,678 clone pairs from SourcererCC into a single set of 2,289 online
clone pairs. There are only 110 common clone pairs between the two clone sets 
as depicted in~\Cref{fig:clonemerging}.  The low number of common
clone pairs is due to SourcererCC reporting clones with method
boundaries while Simian is purely line-based.

@@

\subsubsection{Phase 3-4: Validation and Classification}
We used the 2,289 merged clone pairs for
manual validation and classification.
The validation and classification of the pairs was done at the same time. 
The clone validation process (phase 3 in \Cref{fig:exp_framework}) involves checking 
if a clone pair is a true positive or a false positive. 
Moreover, we are also interested in 
the patterns of code cloning so we can gain more insights into 
how these clones are created (phase 4 in \Cref{fig:exp_framework}).

@@

\vspace{0.25cm}
\textit{How often are Stack Overflow
	answerers aware of the outdated code and 
	licensing conflicts when
	they answer a question on Stack Overflow?} 
\vspace{0.25cm}

@@

We found that although the answerer have been notified of outdated code in their
answers, for 51.5\% of them such notifications occur very rarely (only 1--20\%
of the answers). Only 3 participants reported that they were notified in more
than 60\% of their answers. This notification to the answerer can be done by
posting comments below the answer on Stack Overflow. For example, the answerer of
the Stack Overflow question no.~10924648 posted a comment on his own answer
saying that the answer is specifically for Spring 3.1. Moroever, another user
posted a comment on the answer of the post no.~801935 that the code snippet is
not of high quality and suggested an alternative in another post.

@@

We then asked 131 participants who have been notified of their outdated code a
follow-up question \textit{``how frequently did you fix your outdated code on Stack
	Overflow?''}. The answers, depicted in
\Cref{tab:survey_code_snippet_outdated_fix}, show that more than half of them
(57.2\%) very frequently or frequently fix the outdated code snippets. However,
there are 19.8\% of the answerers in both groups who rarely, very rarely, or never fix 
their outdated code.

The responses from the answerers support our findings of outdated online code
clones in RQ3. The low percentage of outdated code notifications
reflect the experience of high reputation answerers who accumulate the reputation for a
long time. Due to the voting mechanism of Stack Overflow, high reputation users
usually provide high quality answers to earn up votes from other users. They are
careful when posting code snippets in the answer to avoid problems and, vice versa, 
getting down votes. It would be interesting to compare the findings to
Stack Overflow answerers who are newer and have lower reputation. However, we
leave it to future work.

@@

Similar to outdated code, the responses from the answerers support our findings
of licensing conflicts in online code clones in RQ4 and possibly explain why most of
the clones copied from open source projects and external sources do not include
their original software license.

\begin{boxquote}
	To answer RQ 1.1, regarding outdated code, although most of the Stack Overflow answerers are aware that their code
	can be outdated, 51.5\% of the answerers were very rarely notified and 35.5\% have never been notified of
	outdated code in the answers. After being notified, 19.8\% of them rarely or never fix the outdated code.

	For licensing conflicts, 124 answerers out of 200 (62\%) are aware of Stack Overflow's
	CC BY-SA 3.0 license applied to code snippets in questions and answers. However,
	only 3 answerers explicitly include software license in their answers. Some 
	answerers choose to include the license in their profile page instead. 69\% of the
	answerers never check for licensing conflicts between their copied code snippets
	and Stack Overflow's CC BY-SA 3.0.
\end{boxquote}

@@

\textbf{Choice for programming solutions: }
Stack Overflow is ranked higher than official documentation, online
repositories, and books as the resource to look for programming solutions.
Developers rely on Stack Overflow answers because they are easy to search for on
the web. Moreover, 64\% of the participants reuse code snippets from Stack
Overflow at least once a week. They copy code from Stack Overflow because they
can be found easily from search engine, solve similar problems to their
problems, provide helpful context, and offer voting and accepted answers.

\vspace{0.25cm}
\textit{How often do Stack Overflow
	visitors experience the outdated code and licensing conflicts when
	they reuse code in an answer from Stack Overflow?}
\vspace{0.25cm}

@@

In addition, 74 out of the 87 (85\%) participants are not
aware of Stack Overflow CC BY-SA 3.0 license and 62\% never give attributions to
the Stack Overflow posts they copied the code snippets from. 
As shown in \Cref{tab:visitor_survey_license_check}, we found that 66\%
of the visitors never check for software licensing conflicts between Stack
Overflow code snippets and their projects. Interestingly, 9\% of the
participants encountered legal issues. Unfortunately, due to the anonymity of
the survey, we could not investigate further regarding the legal issues that the
participants faced from using Stack Overflow code snippets.

The visitors survey confirms the findings from the previous studies that Stack
Overflow code snippets can be problematic~\cite{Zhang2018,Acar2016,An2017,Fischer2017}. Sixty-six
percent of the visitors experienced a problem from reusing Stack Overflow code
snippets ranging from incorrect solutions, outdated solutions, mismatched
solutions, to buggy code. Although they are aware of the problems, half of them
(56\%) never reports back to the Stack Overflow discussions. On the other hand,
the visitors rarely give attributions to Stack Overflow when they reuse code
snippets from the website, similar to the findings reported
by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
license, and more than half of them never check for license compatibility when
reusing Stack Overflow code snippets. 
Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
check if the code snippet originated from a different source (e.g. an open source project) 
and if they had an incompatible license to their projects.
Moreover, we also found that 9\% of the participants
encountered legal issues by copying code from Stack Overflow. To the best of our
knowledge, a study of legal problems from reusing Stack Overflow code snippets
has never been done before and will be our future work.

@@

The statistics on clones obtained from the merged clone data set are
presented in~\Cref{tab:snippets}. Simian and SourcererCC
reported clones in 460 snippets, approximately 0.6\% of the
72,365 Stack Overflow snippets, associated with 59 Qualitas
projects. For the cloned Stack Overflow snippets, the
average ratio of cloned code is 53.10\% (i.e.\ the number of cloned
lines of the cloned Stack Overflow snippet).

@@

Lastly, during the manual investigation of 2,289 clone pairs, we identified 226 pairs
as being accidental clones (NC), i.e.~false positives. After removing
them, the set still contains 2,076 true positive clone pairs between 443 Stack
Overflow snippets and 59 Qualitas projects. The average cloned ratio for the
true positive clone pairs is 53.89\%.

\begin{boxquote}
	To answer RQ2, we found 2,076 manually confirmed clone pairs between 443 Stack Overflow code snippets
	and 59 Qualitas proejcts. 
	%After the manual confirmation, 2,076 pairs as true positives, i.e.~
	%they are manually confirmed as clones, which 
	%account for 59 Qualitas projects and
	%443 Stack Overflow code snippets.
\end{boxquote}

@@

\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 248 online clone
pairs with evidence of cloning from Qualitas projects to Stack Overflow.
However, we observed that, in some cases, a cloned code snippet on Stack
Overflow matched with more than one code snippet in Qualitas projects because of
code cloning inside Qualitas projects themselves. To avoid double counting of
such online clones, we consolidated multiple clone pairs having the same Stack
Overflow snippet, starting line, and ending line into a single clone pair. We
finally obtained 154 QS pairs (\Cref{tab:classification_good_o}) having unique Stack Overflow code snippets and
associated with 23 Qualitas projects listed in \Cref{tab:qs_qualitas_projects}.
The most cloned project is \textsf{hibernate} with 24
clone pairs, followed by \textsf{eclipse} (21 pairs), \textsf{jung2} (19 pairs),
\textsf{spring} (17 pairs), and \textsf{jfreechart} (13 pairs). The clones are
used as examples and are very similar to their original Qualitas code with
limited modifications. Most of them have a statement in the Stack Overflow post
saying that the code is ``copied'', ``borrowed'' or ``modified'' from a specific
file or class in a Qualitas project. For example, according to the motivating
example in \Cref{fig:before-after}, we found evidence in the Stack Overflow Post
22315734 saying that \textit{``Actually, you can learn how to compare in Hadoop
from WritableComparator. Here is an example that borrows some ideas from it.''}

@@

\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs
found in this study. We observed 1,505 such clone pairs and 217 after
consolidation. The BP clone pairs account for 65\% of all clone pairs we
classified. The majority of them are {\small{\texttt{equals()}}} methods.

@@

\begin{boxquote}
To answer RQ3, we found 154 pairs with
strong evidences to be cloned from 23 Qualitas projects to Stack Overflow, 1 pair
was cloned from Stack Overflow to Qualitas, and
111 pairs were found to be cloned to Stack Overflow from external
sources. However, the largest amount of the clone pairs
between Stack Overflow and Qualitas projects are \linebreak boiler-plate code
(217), followed by 65 clone pairs with no evidence that the code has actually been copied,
and 16 pairs of clones due to implementing the same interface or inheriting the same class.
\end{boxquote}

@@

We analysed code modifications which made Stack Overflow code outdated by going
though commits and git blame information. The six code modification
types found in the 101 outdated online clone pairs are summarised in
\Cref{tab:mod_types}. They include statement addition, statement modification,
statement removal, method rewriting, API change (changing in method signature),
and file deletion. We occasionally found multiple code modifications applied to
one clone pair at the same time but at a different location. The most often code
change found is statement modification (50 occurrences), followed by statement
addition (28 occurrences), statement removal (18 occurrences), change of
method signature, i.e.~API change (16 occurrences), and method rewriting (15
occurrences). Moreover, in the 101 outdated pairs, we found 15 ``dead''
snippets. These snippets cannot be located in the latest version of the
projects. For example, the snippet in Stack Overflow post 3758110, a copy of
{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in \textsf{spring}, was
deleted in the commit
{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on
January 20, 2012, two years after it was posted.

@@

Moreover, using the information in git commit messages, we can associate each
change to its respective issues in an issue tracking system, such as Bugzilla or
Jira. We found that in 58 cases, the cloned code snippets on Stack Overflow were
changed because of a request in the issue tracking system. Since issue tracking
systems are also used, besides bug reports, for feature request and feature
enhancements, having an issue tracking ID can reflect that most of the changes are important
and not only a superficial fix such as code formatting. The intent behind
the changes are grouped into six categories as shown in \Cref{tab:intent_outdated}.
Enhancement are the majority intent accounting for 65 of the 100 outdated code (65\%), followed 
by code deprecation (15\%). There were 10 outdated code snippets (10\%) due to bug fixing.
The rest of the changes are because of code refactoring (6\%), changing coding style (3\%), and 
data format change (2\%).
Not all outdated code are toxic. However, the 10 buggy and outdated code snippets 
we found are toxic and are harmful for reuse.

>>>>

Nevertheless, we investigated a crucial parameter setting for clone detection: 
the minimum clone size threshold.
Choosing a large threshold value can reduce the number of trivial clones
(e.g. \texttt{equals}, \texttt{hashCode}, or getter and setter methods) and
false clones in the analysis or the manual investigation
phase~\cite{Sajnani2016}, while at the same time may create some false negatives,
i.e.~increasing precision. On the other hand, setting a low threshold
results in a larger number of clone candidate pairs to look at, i.e.~increasing recall, 
and a higher chance of getting false positives. 
%It is known that lowering the threshold value 
%is harmful to precision. 
Moreover, the large number of clone
pairs will hinders the full manual validation of the clones.
% and one needs to
%rely on sampling of clone pairs. 
Three threshold values, six, ten, and fifteen lines, were chosen for our
investigation. We started our investigation by using a threshold value of six
lines, a well-accepted minimum clone size in clone benchmark~\cite{Bellon2007}.
Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752
clone candidate pairs. We randomly sampled 382 pairs from the two sets for
manual check. This sample amount was a statistical significant sample with a
95\% confidence level and $\pm 5\%$ confidence interval. The first author
investigated the sampled clone pairs and classified them into three groups:
non-clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
setter methods), and non-trivial clones. The manual check found 26 non-clone
pairs; 322 trivial clone pairs and 34 non-trivial clone pairs. Next, we increased the
threshold to ten lines, another well-established minimum clone size for
large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from
Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and manually
checked the same amount of 382 pairs and found 27 non-clone pairs, 253 trivial
clone pairs and 102 non-trivial clone pairs. Then, we increased the threshold
further to fifteen lines and retrieved 196 clone pairs from Simian and 1,230
clone pairs from SourcererCC. The manual check of the 382 randomly sampled pairs
reveal zero non-clone pairs, 298 trivial clone pairs and 83 non-trivial clone
pairs.

The findings from the three threshold values show that selecting the minimum clone size 
of ten lines was preferred over six and fifteen lines. First, it generated 
a fewer number of clone pairs than using six lines, which made the manual clone
investigation feasible. Second, it preserved the highest number of non-trivial clone
pairs.
%
%The minimum clone size of 10 lines is
%considered a standard setting for clone detection in large-scale data sets to
%avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or getter and
%setter methods) in the analysis or the manual investigation phase~\cite{Sajnani2016}.  
%We
% performed an analysis to confirm this.
%\begin{figure} 
%	\centering
%	\includegraphics[width=\linewidth]{boxplot_clone_size_combined} 
%	\caption{Size of online code clones.} 
%	\label{fig:boxplotclonesize}
%\end{figure}
%
%The result is as shown in
%\Cref{fig:boxplotclonesize}. We found that the distribution of the manually
%confirmed true clones 
%mainly cover the size from about 10 to 20 lines. Increasing
%the threshold to be higher than 10 would remove some of the
%true clone pairs.
%
%Regarding decreasing the minimum clone size to be less than 10 lines, we reran
%the two clone detection tools again using a minimum
%clone size of 6 lines, another well-accepted minimum clone size in clone
%benchmark~\cite{Bellon2007}. Simian reported 67,172 clone candidate pairs and
%SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs. 
%With this large amount of clone
%candidate pairs, it is not feasible to manually confirm all of the clones and we
%must rely on sampling. This will result in weaker findings and
%weaker conclusion. Thus, we decide pick the minimum clone size of 10 lines
%to keep the balance between the number of non-trivial clone pairs and the
%feasibility of manual clone investigation.
%We made sure that they 
%detected only non-trivial clones by increasing the minimum clone size to ten
%lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).
%
%We encountered NiCad failures with a few Qualitas projects.~$N_D$
%could not detect clones in \textsf{hibernate} due to clustering
%errors. $N_E$ generated errors during code normalisation for 5
%projects including \textsf{vuze}, \textsf{hibernate},
%\textsf{myfaces}, \textsf{netbeans}, and \textsf{spring}. We have
%contacted the creator of NiCad regarding the issues. They identified
%the issues as problems in the TXL grammar and as problems of long file
%paths, and will be fixed in the next NiCad releases.
%
The number of online clone pairs reported using the minimum clone size of 10 lines
are presented in \Cref{tab:orig_stats}. Simian reports 721 clone
pairs while SourcererCC reports 1,678 clone pairs. 
%SourcererCC reports more clones due to its capability of detecting
%clones of type-1 to type-3 while Simian only detects type-1 clones.
The average clone size reported by Simian is
16.61 lines which is slightly smaller than SourcererCC (17.86 lines).

@@

The threshold \textit{t} is crucial for the ok-match because it affects the number
of merged clone pairs. Setting a high \textit{t} value will result in a few ok-match clone pairs
and duplicates of the same clone pairs (which are supposed to be merged) may appear in the merged
clone set. On the other hand, setting a low \textit{t} value will result in many ok-match clone
pairs and some non-duplicate clone pairs may be accidentally merged by only
a few matching lines.
In order to get an optimal $t$ value, we did an analysis by choosing
five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
By setting $t=0.7$ according to Bellon's study, we
found 97 ok-match pairs reported. On the other hand, setting $t$ to 0.1, 0.3,
0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually
checked all the 111 reported pairs. We found one false positive pair and 110
true positive pairs. By raising the $t$ to 0.3 and 0.5, we got rid of the false
positive pair and still retained all the 110 true positive pairs. All the clone
pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a
subset of $t=0.5$. However, since there is a fewer true positive pairs reported
(i.e.~generating false negatives), we ended up leaving some duplicates of the 
same clones in the final merged clone set.
With this analysis, we can see that setting the threshold $t$ to 0.1 is too
relaxed and results in having false positive ok-match pairs, while setting the
$t$ to 0.7 or 0.9 is too strict. Thus,
we decided to select the $t$ value at 0.5.

Using the ok-match criterion with the threshold \textit{t} of 0.5
similar to Bellon's study~\cite{Bellon2007}, we merge 721 clone pairs from
Simian and 1,678 clone pairs from SourcererCC into a single set of 2,289 online
clone pairs. There are 110 common clone pairs between the two clone sets 
as depicted in~\Cref{fig:clonemerging}.  The low number of common
clone pairs is due to SourcererCC reporting clones with method
boundaries while Simian is purely line-based.

@@

\subsubsection{Phase 3-4: Validation and Classification}
We used the 2,289 merged clone pairs for
manual validation and online clone classification.
The validation and classification of the pairs was done at the same time. 
The clone validation process (phase 3 in \Cref{fig:exp_framework}) involves checking 
if a clone pair is a true positive or a false positive. 
Moreover, we are also interested in 
the patterns of code cloning so we can gain more insights into 
how these clones are created (phase 4 in \Cref{fig:exp_framework}).

@@

\vspace{0.25cm}
\textit{RQ1.1 How often are Stack Overflow
	answerers aware of the outdated code and 
	licensing conflicts when
	they answer a question on Stack Overflow?} 
\vspace{0.25cm}

@@

We found that although the answerer have been notified of outdated code in their
answers, for 51.5\% of them such notifications occur very rarely (only 1--20\%
of the answers). Only 3 participants reported that they were notified in more
than 60\% of their answers. This notification to the answerer can be done by
posting comments below the answer on Stack Overflow. For example, the answerer of
the Stack Overflow question no.~10924648 posted a comment on his own answer
saying that the answer is specifically for Spring 3.1 and another user
posted a comment on the answer of the post no.~801935 that the code snippet is
not of high quality and suggested an alternative in another post.
The low percentage of outdated code notifications
reflect the experience of high reputation answerers who accumulate the reputation for a
long time. Due to the voting mechanism of Stack Overflow, high reputation users
usually provide high quality answers to earn up votes from other users. They are
careful when posting code snippets in the answer to avoid problems and, vice versa, 
getting down votes. It would be interesting to compare the findings to
Stack Overflow answerers who are newer and have lower reputation. However, we
leave it to future work.

@@

We then asked 131 participants who have been notified of their outdated code a
follow-up question \textit{``how frequently did you fix your outdated code on Stack
	Overflow?''}. The answers, depicted in
\Cref{tab:survey_code_snippet_outdated_fix}, show that more than half of them
(57.2\%) very frequently or frequently fix the outdated code snippets. However,
there are 19.8\% of the answerers in both groups who rarely, very rarely, or never fix 
their outdated code.
%
%The responses from the answerers support our findings of outdated online code
%clones in RQ3.

@@

%Similar to outdated code, the responses from the answerers support our findings
%of licensing conflicts in online code clones in RQ4 and possibly explain why most of
%the clones copied from open source projects and external sources do not include
%their original software license.

\begin{boxquote}
	To answer RQ 1.1, although most of the Stack Overflow answerers are aware that their code
	can be outdated, half of the answerers were very rarely notified of
	outdated code in the answers. After being notified, some of them rarely or never fix the outdated code.
	More than half of the answerers are aware of Stack Overflow's
	CC BY-SA 3.0 license. Only 3 answerers explicitly include software license in their answers
	while some of them choose to include the license in their profile page instead. More than half of the
	answerers never check for licensing conflicts between their copied code snippets
	and Stack Overflow's CC BY-SA 3.0.
\end{boxquote}

@@

\textbf{Choice for programming solutions: }
Stack Overflow is ranked higher than official documentation, online
repositories, and books as the resource to look for programming solutions.
Developers rely on Stack Overflow answers because they are easy to search for on
the web. Moreover, 64\% of the participants reuse code snippets from Stack
Overflow at least once a week. They copy code from Stack Overflow because they
can be found easily from search engine, solve similar problems to their
problems, provide helpful context, and offer voting mechanism and accepted answers.

\vspace{0.25cm}
\textit{RQ1.2 How often do Stack Overflow
	visitors experience the outdated code and licensing conflicts when
	they reuse code in an answer from Stack Overflow?}
\vspace{0.25cm}

@@

In addition, 74 out of the 87 (85\%) participants are not
aware of Stack Overflow CC BY-SA 3.0 license and 62\% never give attributions to
the Stack Overflow posts they copied the code snippets from. 
As shown in \Cref{tab:visitor_survey_license_check}, we found that 66\%
of the visitors never check for software licensing conflicts between Stack
Overflow code snippets and their projects. Interestingly, 9\% of the
participants encountered legal issues. Due to the anonymity of
the survey, we could not investigate further regarding the legal issues that the
participants faced from using Stack Overflow code snippets.
To the best of our
knowledge, a study of legal problems from reusing Stack Overflow code snippets
has never been done before and will be our future work.

%The visitors survey confirms the findings from the previous studies that Stack
%Overflow code snippets can be problematic~\cite{Zhang2018,Acar2016,An2017,Fischer2017}. 
%Sixty-six
%percent of the visitors experienced a problem from reusing Stack Overflow code
%snippets ranging from incorrect solutions, outdated solutions, mismatched
%solutions, to buggy code. Although they are aware of the problems, half of them
%(56\%) never reports back to the Stack Overflow discussions. On the other hand,
%the visitors rarely give attributions to Stack Overflow when they reuse code
%snippets from the website, similar to the findings reported
%by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
%license, and more than half of them never check for license compatibility when
%reusing Stack Overflow code snippets. 
%Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
%check if the code snippet originated from a different source (e.g. an open source project) 
%and if they had an incompatible license to their projects.
%Moreover, we also found that 9\% of the participants
%encountered legal issues by copying code from Stack Overflow.

@@

The statistics on clones obtained from the merged clone data set are
presented in~\Cref{tab:snippets}. Simian and SourcererCC
reported clones in 460 snippets, approximately 0.6\% of the
72,365 Stack Overflow snippets, associated with 59 Qualitas
projects. For the cloned Stack Overflow snippets, the
average ratio of cloned code is 53.28\% (i.e.\ the number of cloned
lines of the cloned Stack Overflow snippet).

@@

Lastly, during the manual investigation of 2,289 clone pairs, we identified 226 pairs
as being accidental clones (NC), i.e.~false positives. After removing
them, the set still contains 2,063 true positive clone pairs between 443 Stack
Overflow snippets and 59 Qualitas projects. The average cloned ratio for the
true positive clone pairs is 54.09\%.

\begin{boxquote}
	To answer RQ2, we found 2,063 manually confirmed clone pairs between 443 Stack Overflow code snippets
	and 59 Qualitas proejcts. 
	%After the manual confirmation, 2,076 pairs as true positives, i.e.~
	%they are manually confirmed as clones, which 
	%account for 59 Qualitas projects and
	%443 Stack Overflow code snippets.
\end{boxquote}

@@

\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 247 online clone
pairs with evidence of cloning from Qualitas projects to Stack Overflow.
However, we observed that, in some cases, a cloned code snippet on Stack
Overflow matched with more than one code snippet in Qualitas projects because of
code cloning inside Qualitas projects themselves. To avoid double counting of
such online clones, we consolidated multiple clone pairs having the same Stack
Overflow snippet, starting line, and ending line into a single clone pair. We
finally obtained 153 QS pairs (\Cref{tab:classification_good_o}) having unique Stack Overflow code snippets and
associated with 23 Qualitas projects listed in \Cref{tab:qs_qualitas_projects}.
The most cloned project is \textsf{hibernate} with 23
clone pairs, followed by \textsf{eclipse} (21 pairs), \textsf{jung2} (19 pairs),
\textsf{spring} (17 pairs), and \textsf{jfreechart} (13 pairs). The clones are
used as examples and are very similar to their original Qualitas code with
limited modifications. Most of them have a statement in the Stack Overflow post
saying that the code is ``copied'', ``borrowed'' or ``modified'' from a specific
file or class in a Qualitas project. For example, according to the motivating
example in \Cref{fig:before-after}, we found evidence in the Stack Overflow Post
22315734 saying that \textit{``Actually, you can learn how to compare in Hadoop
from WritableComparator. Here is an example that borrows some ideas from it.''}

@@

\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs
found in this study. We observed 1,495 such clone pairs and 216 after
consolidation. The BP clone pairs account for 65\% of all clone pairs we
classified. The majority of them are {\small{\texttt{equals()}}} methods.

@@

\begin{boxquote}
To answer RQ3, we found 153 pairs with
strong evidences to be cloned from 23 Qualitas projects to Stack Overflow, 1 pair
was cloned from Stack Overflow to Qualitas, and
109 pairs were found to be cloned to Stack Overflow from external
sources. However, the largest amount of the clone pairs
between Stack Overflow and Qualitas projects are \linebreak boiler-plate code
(216), followed by 65 clone pairs with no evidence that the code has actually been copied,
and 9 pairs of clones due to implementing the same interface or inheriting the same class.
\end{boxquote}

@@

We analysed code modifications which made Stack Overflow code outdated by going
though commits and git blame information. The six code modification
types found in the 100 outdated online clone pairs are summarised in
\Cref{tab:mod_types}. They include statement addition, statement modification,
statement removal, method rewriting, API change (changing in method signature),
and file deletion. We occasionally found multiple code modifications applied to
one clone pair at the same time but at a different location. The most often code
change found is statement modification (50 occurrences), followed by statement
addition (28 occurrences), statement removal (18 occurrences), change of
method signature, i.e.~API change (16 occurrences), and method rewriting (15
occurrences). Moreover, in the 101 outdated pairs, we found 15 ``dead''
snippets. These snippets cannot be located in the latest version of the
projects. For example, the snippet in Stack Overflow post 3758110, a copy of
{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in \textsf{spring}, was
deleted in the commit
{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on
January 20, 2012, two years after it was posted.

@@

Moreover, using the information in git commit messages, we can associate each
change to its respective issues in an issue tracking system, such as Bugzilla or
Jira. We found that in 58 cases, the cloned code snippets on Stack Overflow were
changed because of a request in the issue tracking system. Since issue tracking
systems are also used, besides bug reports, for feature request and feature
enhancements, having an issue tracking ID can reflect that most of the changes are important
and not only a superficial fix such as code formatting. The intent behind
the changes are grouped into six categories as shown in \Cref{tab:intent_outdated}.
Enhancement are the majority intent accounting for 65 of the 100 outdated code (65\%), followed 
by code deprecation (15\%). There were 10 outdated code snippets (10\%) caused by bug fixing.
The rest of the changes are because of code refactoring (6\%), changing coding style (3\%), and 
data format change (2\%).
Not all outdated code are toxic. However, the 10 buggy and outdated code snippets 
we found are toxic and are harmful for reuse.
